---
title: "Programming with R"
author: "Ronny A. Hernández Mora"
date: "12/09/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# If you don´t have the packages, run the followin:

# install.packages(c("dplyr", "purrr", "janitor",
#                    "readr", "tidyr", "lubridate",
#                    "googlesheets4", "fs"))

# Load R packages
library(dplyr)
library(purrr)
library(janitor)
library(readr)
library(tidyr)
library(lubridate)
library(fs)

# Load internal functions
source("R/prepare_examples.R")
```

# Reading files

We can read many data files in R. There are several packages to do this and it
depends on the file extension. 

Let's prepare our data for examples. Run the following code to set your data
example files:
```{r prepare_examples}
prepare_examples()
```

Now that we have our example data files (check the new folder 'data') we are
going to read the 'principe_2015.csv' data file:

```{r read_one_file}
# Read the .csv file
principe <- read_csv("data/principe_2015.csv")

# Chech the content
glimpse(principe)
```

Now, what happens if we need to read all the principe files?
```{r read_many_files}
dir_ls("data")

# Create object with files of interest
files <- dir_ls(path = "data", glob = "data/principe_*")
```

Now, we can iterate on each file to read it
```{r iterate_read}
read_files <- map(files, read_csv)
```

But we want one data frame, not a list
```{r map_dataframe}
principe <- files %>% 
  map_dfr(~read_csv(.x))

principe <- files %>% 
  map_dfr(read_csv, .id = "check")
```

We can many data file types. Even we can read file directly from our google 
drive:

```{r read_from_drive}
principe_drive <- read_sheet("1e6_LeSP9LjDBFSKvcCbM3yoUhLOCSK2_SqmkoAl7nzo")
```

# Export objects

We can not only read from google sheets, we can also write to a google sheet

```{r write_to_drive}

```

